### 2021-02-22 ch04_papers_ecs_tcr_assessment/papers_ecs_tcr_assessment.tex
Finished section 6.2

However, it is well-known that the low-level mixed-phase clouds over the
Southern Ocean in these earlier climate models are biased towards too large
amounts of ice crystals and too little amounts of supercooled liquid water
\autocite{BodasSalcedo2016, McCoy2015, McCoy2016, Tan2016}. For this reason,
the microphysical representation of mixed-phase clouds has been substantially
improved in many \acs{CMIP}6 models \autocite{BodasSalcedo2019, Gettelman2019,
  Mulcahy2020, Williams2020}, leading for example to a better agreement of the
simulated \ac{TOA} shortwave \ac{CRE} with corresponding observations
\autocite{Bock2020}. As a consequence, the strong negative cloud feedback
described above that results from a cloud phase change from ice clouds in the
present-day to liquid clouds in the future is removed (or significantly
reduced) in those \acs{CMIP}6 models that simulate predominantly liquid clouds
over the present-day Southern Ocean. This is illustrated in
\cref{fig:04:cloud_phase_change_feedback} (orange arrows). Moreover, this
reduction of the negative shortwave cloud phase change feedback increases the
global net cloud feedback \autocite{BodasSalcedo2019, Tan2016} and eventually
the \ac{ECS} of the affected \acs{CMIP}6 models \autocite{Andrews2019,
  Gettelman2019}, offering a possible explanation for the high \ac{ECS} values
in some \acs{CMIP}6 models.

>>>>

However, it is well known that the low-level mixed-phase clouds over the
Southern Ocean in these earlier climate models are biased towards too large
amounts of ice crystals and too little amounts of supercooled liquid water
\autocite{BodasSalcedo2016, McCoy2015, McCoy2016, Tan2016}. For this reason,
the microphysical representation of mixed-phase clouds has been substantially
improved in many \acs{CMIP}6 models \autocite{BodasSalcedo2019, Gettelman2019,
  Mulcahy2020, Williams2020}, leading for example to a better agreement of the
simulated \ac{TOA} shortwave \ac{CRE} with corresponding observations
\autocite{Bock2020}. As a consequence, the strong negative cloud feedback
described above that results from a cloud phase change from ice clouds in the
present-day to liquid clouds in the future is removed (or significantly
reduced) in those \acs{CMIP}6 models that simulate predominantly liquid clouds
over the present-day Southern Ocean. This is illustrated in
\cref{fig:04:cloud_phase_change_feedback} (orange arrows). Moreover, this
reduction of the negative shortwave cloud phase change feedback increases the
global net cloud feedback \autocite{BodasSalcedo2019, Tan2016} and eventually
the \ac{ECS} of the affected \acs{CMIP}6 models \autocite{Andrews2019,
  Gettelman2019}, offering a possible explanation for the high \ac{ECS} values
in some \acs{CMIP}6 models.

### 2021-02-22 ch06_paper_gpp/paper_gpp.tex
Finished section 6.2

To get a detailed insight into the performance of our \ac{GBRT} model, we
compare it to five other statistical models: the unweighted \acs{CMIP}5
\ac{MMM} of future \ac{GPP} (\acs{MMM}), its rescaled version using
\cref{eq:06:y} (r\acs{MMM}), a linear \ac{LASSO} regression model using all
features as defined in \cref{tab:06:predictors} (\ac{LASSO}), a
single-predictor \ac{LASSO} model (\acs{LASSO}-1D) and a single-predictor
\ac{GBRT} model (\acs{GBRT}-1D). Both single-predictor models use the
historical \ac{GPP} as only feature. The predictive power (in terms of
\ac{RMSEP}) of each statistical model is assessed using the leave-one-model-out
\ac{CV} approach (see \cref{subsec:06:uncertainty_and_skill}). This allows us
to create an \ac{RMSEP} distribution for each statistical approach, where the
different points of the distributions refer to different training/prediction
dataset combinations generated by the leave-one-model-out \ac{CV} approach.
Thus, each distribution consists of seven points, one for each climate model.
\Cref{fig:06:step2a_ml_inference:a} shows the \ac{RMSEP} distributions for the
six different statistical models.

@@

In terms of raw predictive power, the simple \ac{MMM} is outperformed by every
other model. Its prediction uncertainty expressed as mean \ac{RMSEP} can be
reduced by more than $48 \unit{\%}$ by using other statistical models. However,
this is not surprising: In contrast to the other statistical models, the simple
\acs{RCP}8.5 \ac{MMM} does not take further evidence in form of observations of
the historical climate into account. Step 1 of our algorithm (r\acs{MMM}) can
reduce this mean \ac{RMSEP} by $15 \unit{\%}$ due to the simple rescaling of
the gridded climate model output with the global mean \ac{GPP} constraint on
the \ac{CO2} fertilization effect. However, since there is a considerably large
\ac{GPP} range in the individual climate models themselves, this reduction is
rather small for the gridded values. A far larger reduction of the \ac{RMSEP}
can be achieved by using the regression models \acs{LASSO}‐1D, \ac{LASSO},
\acs{GBRT}‐1D and \ac{GBRT}. All of them share similar \ac{RMSEP}
distributions, which can be explained as follows: The historical \ac{GPP} is
strongly (near linearly) correlated to the rescaled end-of-century \ac{GPP}
(with pattern correlation of $R^2 = 0.83$ for the whole multi-model ensemble).
Because of that, all regression models are able to considerably reduce the
\acp{RMSEP} compared to the \acs{MMM} and r\acs{MMM}. This also shows that the
\ac{GBRT} models successfully learn the linear connection between past and
future \ac{GPP}. Moreover, the non-linear \ac{GBRT} models can slightly reduce
the mean \ac{RMSEP} even further compared to the linear \ac{LASSO} models by
about $2 \unit{\%}$ for \acs{GBRT}‐1D and $3 \unit{\%}$ for the full \ac{GBRT}
model. This leads to the conclusion that in addition to the strong linear
relationship between past and future \ac{GPP}, there are small non-linear
relations between the predictors and the target variable that can be used to
further reduce the \ac{RMSEP}. Since the full \ac{GBRT} model with access to
all predictors shows the minimal mean \ac{RMSEP}, we argue that it is
beneficial for our approach to use the multivariate non-linear \ac{GBRT} model
instead of a linear model because only the \ac{GBRT} algorithm is able to make
use of all predictors and exploit more complex relationships.

@@

The result of step 1 on the gridded data is illustrated in
\cref{fig:06:step2a_results:a}, which shows the ratio between r\acs{MMM} and
\acs{MMM}. This ratio is almost constant over the whole globe, which is not
surprising due to the global nature of the rescaling (see \cref{eq:06:y}). The
use of the global emergent constraint predicts a slightly lower \ac{GPP}
increase over the \nth{21} century ($39 \unit{\%}$) than the unweighted
\acs{CMIP}5 ensemble mean ($43 \unit{\%}$). The corresponding ratio $39
\unit{\%} / 43 \unit{\%} \approx 0.91$ is approximately equal to the mean value
of r\acs{MMM}/\acs{MMM} ($0.92$). Consequently, the global estimate of
r\acs{MMM} gives a lower \ac{GPP} at the end of the century ($179
\unit{\GtCyr{}}$) as \acs{MMM} ($198 \unit{\GtCyr{}}$), which can be
interpreted as a correction of the \acp{ESM}' overestimation of future \ac{GPP}
to changes in the atmospheric \ac{CO2} concentration.

@@

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9a.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:a}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9b.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:b}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9c.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:c}
  \end{subfigure}
  \caption{(a) Ratio of the rescaled \acs{CMIP}5 ensemble mean of the
    fractional change in \acf{GPP} over the \nth{21} century using
    \cref{eq:06:y} (r\acs{MMM}; see \cref{fig:06:step2b_results:b}) and its
    unweighted version (\acs{MMM}; see \cref{fig:06:step2b_results:a}). The
    plot shows an almost constant value over the whole globe with a mean of
    $0.91$, which corresponds to the ratio of the constrained global mean
    \acs{GPP} change over the \nth{21} century from step 1 ($39 \unit{\%}$)
    and the \acs{CMIP}5 ensemble mean global mean GPP change ($43 \unit{\%}$).
    All values close to $0$ for the dataset in the denominator have been
    masked to avoid divisions by $0$. Absolute (b) and relative (c)
    differences between the fractional \acs{GPP} change over the \nth{21}
    century predicted by the \acf{GBRT} model (see
    \cref{fig:06:step2b_results:d}) and r\acs{MMM} (see
    \cref{fig:06:step2b_results:b}). For panel (c), all values close to $0$ for
    the dataset in the denominator have been masked to avoid divisions by $0$.
    Both plots show a good agreement over large parts of the globe
    (corresponding to values of $0$). There are large absolute differences in
    the Sahara region and central Asia. The largest relative differences
    (except for the Sahara and Arabian Peninsula region) appear over South
    America, South Africa, the west coast of Africa, the Middle East, parts of
    Australia and western parts of the United States.
    \AdaptedFrom{Schlund2020}.}
  \label{fig:06:step2b_results_biases}
\end{figure}

>>>>

To get a detailed insight into the performance of our \ac{GBRT} model, we
compare it to five other statistical models: the unweighted \acs{CMIP}5
\ac{MMM} of future \ac{GPP}, its rescaled version using \cref{eq:06:y}
(r\acs{MMM}), a linear \ac{LASSO} regression model using all features as
defined in \cref{tab:06:predictors}, a single-predictor \ac{LASSO} model
(\acs{LASSO}-1D) and a single-predictor \ac{GBRT} model (\acs{GBRT}-1D). Both
single-predictor models use the historical \ac{GPP} as only feature. The
predictive power (in terms of \ac{RMSEP}) of each statistical model is assessed
using the leave-one-model-out \ac{CV} approach (see
\cref{subsec:06:uncertainty_and_skill}). This allows us to create an \ac{RMSEP}
distribution for each statistical approach, where the different points of the
distributions refer to different training/prediction dataset combinations
generated by the leave-one-model-out \ac{CV} approach. Thus, each distribution
consists of seven points, one for each climate model.
\Cref{fig:06:step2a_ml_inference:a} shows the \ac{RMSEP} distributions for the
six different statistical models.

@@

In terms of raw predictive power, the simple \ac{MMM} is outperformed by every
other model. Its prediction uncertainty expressed as mean \ac{RMSEP} can be
reduced by more than $48 \unit{\%}$ by using other statistical models. However,
this is not surprising: In contrast to the other statistical models, the simple
\acs{RCP}8.5 \ac{MMM} does not take further evidence in form of observations of
the historical climate into account. Step 1 of our algorithm (r\acs{MMM}) can
reduce this mean \ac{RMSEP} by $15 \unit{\%}$ due to the simple rescaling of
the gridded climate model output with the global mean \ac{GPP} constraint on
the \ac{CO2} fertilization effect. However, since there is a considerably large
\ac{GPP} range in the individual climate models themselves, this reduction is
rather small for the gridded values. A far larger reduction of the \ac{RMSEP}
can be achieved by using the regression models \acs{LASSO}‐1D, \ac{LASSO},
\acs{GBRT}‐1D and \ac{GBRT}. All of them share similar \ac{RMSEP}
distributions, which can be explained as follows: The historical \ac{GPP} is
strongly (near linearly) correlated to the rescaled end-of-century \ac{GPP}
(with pattern correlation of $R^2 = 0.83$ for the whole multi-model ensemble).
Because of that, all regression models are able to considerably reduce the
\acp{RMSEP} compared to the \ac{MMM} and r\acs{MMM}. This also shows that the
\ac{GBRT} models successfully learn the linear connection between past and
future \ac{GPP}. Moreover, the non-linear \ac{GBRT} models can slightly reduce
the mean \ac{RMSEP} even further compared to the linear \ac{LASSO} models by
about $2 \unit{\%}$ for \acs{GBRT}‐1D and $3 \unit{\%}$ for the full \ac{GBRT}
model. This leads to the conclusion that in addition to the strong linear
relationship between past and future \ac{GPP}, there are small non-linear
relations between the predictors and the target variable that can be used to
further reduce the \ac{RMSEP}. Since the full \ac{GBRT} model with access to
all predictors shows the minimal mean \ac{RMSEP}, we argue that it is
beneficial for our approach to use the multivariate non-linear \ac{GBRT} model
instead of a linear model because only the \ac{GBRT} algorithm is able to make
use of all predictors and exploit more complex relationships.

@@

The result of step 1 on the gridded data is illustrated in
\cref{fig:06:step2a_results:a}, which shows the ratio between r\acs{MMM} and
\ac{MMM}. This ratio is almost constant over the whole globe, which is not
surprising due to the global nature of the rescaling (see \cref{eq:06:y}). The
use of the global emergent constraint predicts a slightly lower \ac{GPP}
increase over the \nth{21} century ($39 \unit{\%}$) than the unweighted
\acs{CMIP}5 ensemble mean ($43 \unit{\%}$). The corresponding ratio $39
\unit{\%} / 43 \unit{\%} \approx 0.91$ is approximately equal to the mean value
of r\acs{MMM}/\acs{MMM} ($0.92$). Consequently, the global estimate of
r\acs{MMM} gives a lower \ac{GPP} at the end of the century ($179
\unit{\GtCyr{}}$) as \ac{MMM} ($198 \unit{\GtCyr{}}$), which can be
interpreted as a correction of the \acp{ESM}' overestimation of future \ac{GPP}
to changes in the atmospheric \ac{CO2} concentration.

@@

\subsection{Constraining Gridded Fractional \acs{GPP} Change Projections (Step
  2b)}
\label{subsec:06:results_step2b}

In step 2b, we constrain the gridded fractional \ac{GPP} change over the
\nth{21} century (2100 versus 2000) in the emission-driven \acs{RCP}8.5
scenario (rescaled using \cref{eq:06:y}). This step is independent from step 2a
and only differs in the target variable (\ac{GPP} change instead of absolute
\ac{GPP}). The remaining setup including the predictors, the \ac{GBRT} model
itself and the datasets are similar.

\subsubsection{Prediction Error in Leave‐One‐Model‐Out \acs{CV} Approach and
  Feature Importance}
\label{subsubsec:06:results_step2b_ml_inference}

\Cref{fig:06:step2b_ml_inference:a} shows the \ac{RMSEP} distributions for four
different statistical models: the simple \acs{CMIP}5 \ac{MMM} of the fractional
\ac{GPP} change, its rescaled version using \cref{eq:06:y} (r\acs{MMM}), a
linear \ac{LASSO} regression model and the \ac{GBRT} model. Similar to step 2a,
the \ac{GBRT} approach shows the smallest mean \ac{RMSEP} values of all
statistical models. Compared to \ac{MMM} and r\acs{MMM} the mean is reduced by
$16 \unit{\%}$ and $9 \unit{\%}$, respectively. Moreover, the non-linear
\ac{GBRT} model also outperforms the linear \ac{LASSO} model (mean reduced by
$3 \unit{\%}$). In contrast to step 2a, there is not a single predictor which
heavily dominates the feature importance of the \ac{GBRT} model. Thus, using
single-predictor models (\acs{GBRT}‐1D and \acs{LASSO}‐1D) is not necessary in
step 2b. \Cref{fig:06:step2b_ml_inference:b,fig:06:step2b_ml_inference:d} show
the global feature importance for the \ac{LASSO} and \ac{GBRT} model,
respectively. Both models agree that the \acf{T} and \ac{LAI} are the two
dominant predictors with a relative importance of more than $65 \unit{\%}$. The
\ac{LASSO} model shows a relative importance of less than $10 \unit{\%}$ for
each of the remaining features, while the \ac{GBRT} model exhibits a
considerably high relative importance for \ac{GPP} with almost $20 \unit{\%}$.
All predictors are negatively correlated to the target variable (as given by
the sign of the linear Pearson correlation coefficient). That means cold areas
with a small \ac{LAI} in the historical climate show a larger \ac{GPP} change
over the \nth{21} century and vice versa. Indeed, the fertilization effect is
expected to be stronger in lower \ac{LAI} regions. To get more detailed
insights on this, observation-driven data is fed into the \ac{GBRT} model to
obtain a constrained fractional \ac{GPP} change over the \nth{21} century.

\subsubsection{Observation-Based \acs{GBRT} Prediction of Relative \acs{GPP}}
\label{subsubsec:06:results_step2b_obs}

The global distribution of the fractional \ac{GPP} change for the different
statistical models is shown in \cref{fig:06:step2b_results}. All panels show a
\ac{GPP} increase over the \nth{21} century in the \acs{RCP}8.5 scenario for
almost all regions of the globe. Compared to the unweighted \acs{CMIP}5
\ac{MMM}, its rescaled version (r\acs{MMM}) shows a slightly lower \ac{GPP}
increase, which is consistent with the emergent constraint approach from step 1
that shows a lower global mean \ac{GPP} increase over the \nth{21} century ($39
\unit{\%}$) than the global \acs{CMIP}5 ensemble mean ($43 \unit{\%}$). This is
also illustrated in \cref{fig:06:step2b_results_biases:a}, which shows an
almost constant pattern over the whole globe with a mean of $0.91$ that is
consistent with the ratio $39 \unit{\%} / 43 \unit{\%} \approx 0.91$. Similar
to step 2a, this can be interpreted as a global correction of the \acp{ESM}'
response of future \ac{GPP} to changes in the atmospheric \ac{CO2}
concentration.

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9a.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:a}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9b.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:b}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/9c.pdf}
    \caption{}
    \label{fig:06:step2b_results_biases:c}
  \end{subfigure}
  \caption{(a) Ratio of the rescaled \acs{CMIP}5 ensemble mean of the
    fractional change in \acf{GPP} over the \nth{21} century using
    \cref{eq:06:y} (r\acs{MMM}; see \cref{fig:06:step2b_results:b}) and its
    unweighted version (\acs{MMM}; see \cref{fig:06:step2b_results:a}). The
    plot shows an almost constant value over the whole globe with a mean of
    $0.91$, which corresponds to the ratio of the constrained global mean
    \acs{GPP} change over the \nth{21} century from step 1 ($39 \unit{\%}$)
    and the \acs{CMIP}5 ensemble mean global mean GPP change ($43 \unit{\%}$).
    All values close to $0$ for the dataset in the denominator have been
    masked to avoid divisions by $0$. Absolute (b) and relative (c)
    differences between the fractional \acs{GPP} change over the \nth{21}
    century predicted by the \acf{GBRT} model (see
    \cref{fig:06:step2b_results:d}) and r\acs{MMM} (see
    \cref{fig:06:step2b_results:b}). For panel (c), all values close to $0$ for
    the dataset in the denominator have been masked to avoid divisions by $0$.
    Both plots show a good agreement over large parts of the globe
    (corresponding to values of $0$). There are large absolute differences in
    the Sahara region and central Asia. The largest relative differences
    (except for the Sahara and Arabian Peninsula region) appear over South
    America, South Africa, the west coast of Africa, the Middle East, parts of
    Australia and western parts of the United States.
    \AdaptedFrom{Schlund2020}.}
  \label{fig:06:step2b_results_biases}
\end{figure}

All four patterns of \cref{fig:06:step2b_results} show very similar
geographical patterns. Obvious exceptions are the Sahara desert and the Arabian
Peninsula, which show a noisy behavior for the \aclp{MMM} (\ac{MMM} and
r\acs{MMM}) and a small \ac{GPP} increase for the two regression models
(\ac{LASSO} and \ac{GBRT}). This noise-like pattern occurs due to numerical
inconsistencies produced by very small values in the absolute historical and
future \ac{GPP} in the climate models in this region that are used to derive
the fractional \ac{GPP} change following \cref{eq:06:f}. However, due to the
small impact on the global mean \ac{GPP}, this region is negligible in our
analysis. The fractional \ac{GPP} change is not uniformly distributed over the
globe. Instead, there is a pronounced latitudinal dependency in its
geographical pattern: In high latitudes, the projected \ac{GPP} change is
larger than in regions closer to the equator. This effect is particularly
strong for the northern high latitudes and consistent with the results of
\textcite{Wenzel2016}, who find an increased \ac{GPP} change in northern
high-latitude ecosystems compared to the northern extratropics. A possible
reason for this is the extension of the growing season in high latitudes caused
by climate change connected to a \emph{greening}, which has already been
observed in the past climate through satellite measurements
\autocite{Lucht2002, Myneni1997, Zhang2020} and associated with the increase in
the \ac{CO2} seasonal cycle amplitude \autocite{Forkel2016}. This is consistent
with the feature map in \cref{fig:06:step2b_ml_inference:c}, which shows an
increased relative importance of the \ac{LAI} (a quantity directly related to
the greening) in the high-latitude regions with high \ac{GPP} changes. On the
contrary, in the tropical ecosystems the growing season already covers the
whole year. Thus, a further climate change--induced extension is not possible,
leading to a smaller fractional \ac{GPP} change in regions closer to the
equator. For most parts of the remaining globe, \ac{T} is the dominant
predictor, with some areas in northern Africa, the Middle East, India and
Australia showing an increased relative importance of the historical \ac{GPP}.
Overall, the negative correlation of the three most important features (\ac{T},
\ac{LAI}, and historical \ac{GPP}) to the target variable is well reflected in
the global pattern of the fractional \ac{GPP} change: The high latitudes with
lower \ac{T}, lower \ac{LAI} and lower historical \ac{GPP} show higher \ac{GPP}
changes, whereas regions closer to the equator with higher \ac{T}, higher
\ac{LAI} and higher historical \ac{GPP} show smaller \ac{GPP} changes. At this
point we want to emphasize that it is not possible to infer global or other
large-scale averages of the fractional \ac{GPP} change from the geographical
distributions in \cref{fig:06:step2b_results} since division operations and
averaging operations do not commute: in general, $\sum_i \left( a_i / b_i
\right) \neq \left( \sum_i a_i \right) / \left( \sum_i b_i \right)$. Thus, a
direct comparison to other studies that give locally or globally aggregated
results is not possible.

To get further insights in the \ac{GBRT} algorithm, we compare it directly to
the rescaled \acs{CMIP}5 \ac{MMM} (r\acs{MMM}), which is illustrated in
\cref{fig:06:step2b_results_biases:b,fig:06:step2b_results_biases:c}. The
mismatch between \ac{GBRT} and r\acs{MMM} can be interpreted as additional
information that is added to the target variable by the observations in the
predictors in step 2b. Overall, the absolute difference
(\cref{fig:06:step2b_results_biases:b}) is small over the whole globe,
indicating that the r\acs{MMM} and \ac{GBRT} agree in the general pattern of
the fractional \ac{GPP} change. The most striking deviation in this panel is
again the Sahara and Arabian Peninsula region, which shows the already
discussed large absolute differences. Apart from that, there is a large patch
in central Asia that shows high negative differences, that is, the \ac{GBRT}
model predicts a smaller \ac{GPP} change in this area. The relative difference
(\cref{fig:06:step2b_results_biases:c}) indicates many regions where the
\ac{GBRT} model predicts an increased \ac{GPP} change compared to r\acs{MMM},
in particular South America, South Africa, the west coast of Africa, the Middle
East, parts of Australia and western parts of the United States. However, all
these correspond to low absolute \ac{GPP} changes.
\Cref{fig:app:b:step2b_results_errors} shows the corresponding gridded
uncertainties for all four statistical models that also cover the uncertainty
in the emergent constraint and the observational uncertainty (in contrast to
\cref{fig:06:step2b_ml_inference:a}, which only covers the uncertainty in the
statistical models). Similar to step 2a, the local standard errors are large,
even for the \ac{GBRT} model (that performs better than any other statistical
model) which shows errors of at least $43.6 \unit{\%}$ for every grid cell
caused by the uncertainty in the statistical model itself.
\Cref{fig:app:b:residuals:b} illustrates the residuals for the training and
independent test datasets and shows that the \ac{GBRT} model has symmetrical
residuals and is not overfitting.

\subsection{Comparison of the Absolute and Relative \acs{GBRT} Prediction}
\label{subsec:06:comparison_step2a_step2b}

In a last step, we use the FLUXNET‐MTE observational product to constrain the
absolute \ac{GPP} increase at the end of the \nth{21} century
(\range{2091}{2100}) from the fractional \ac{GPP} change given by the \ac{GBRT}
model in step 2b. This can be directly compared to the output of step 2a and
serves as a sanity check between steps 2a and 2b. As shown by
\cref{fig:06:comparison_step2a_step2b}, both approaches show similar
geographical patterns (pattern correlation: $R^2 = 0.97$). The difference
between the two approaches is in the same order of magnitude as the difference
between the different statistical models used in step 2a (see
\cref{fig:06:step2a_results_biases:c,fig:06:step2a_results_biases:d}) and
considerably smaller than the difference between the \ac{GBRT} and r\acs{MMM}
approaches (see \cref{fig:06:step2a_results:b}). Moreover, the globally
aggregated results ($169 \unit{\GtCyr{}}$ for step 2a and $175 \unit{\GtCyr{}}$
for step 2b) are both compatible with the global value of
$\pmrangeunit{171}{12}{\GtCyr{}}$ given by the global emergent constraint in
step 1.
